\begin{thebibliography}{}
\bibitem{report}
Internet Society Global Internet Report 2015.
\textit{http://www.internetsociety.org/globalinternetreport/
assets/download/IS\_web.pdf}.
\bibitem{stats}
Internet stats \& facts for 2016
\textit{https://hostingfacts.com/internet-facts-stats-2016/}
\bibitem{Labovitz}
C. Labovitz, S. Lekel-Johnson, D. McPherson, J. Oberheide, and F. Jahanian. 
\textit{Internet Inter-Domain Traffic}.
In Proc. ACM SIGCOMM, 2010.
\bibitem{Poese}
I. Poese, B. Frank, B. Ager, G. Smaragdakis, and A. Feldmann.
\textit{Improving Content Delivery using Provider-Aided Distance. Information}. 
In ACM IMC, 2010.
\bibitem{Manuel}
Manuel Palacin, Miquel Oliver, Jorge Infante, Simon Oechsner and Alex
Bikfalvi 
\textit{The Impact of Content Delivery Networks on the Internet Ecosystem}.
Journal of Information Policy, Vol. 3 (2013), pp. 304-330

\bibitem{Schonfeld}
Schonfeld, E. Eric Schmidts 
\textit{Gang Of Four:Google, Apple,Amazon,And Facebook}.
TechCrunch.Retrieved from https://techcrunch.com/2011/05/31/schmidt-gang-four-google-apple-amazon-facebook/
\bibitem{Shavitt}
Y. Shavitt and U. Weinsberg
\textit{“Topological trends of Internet content providers”}
in Proceedings of the 4th Annual Workshop
on Simplifying Complex Networks for Practitioners (SIMPLEX
’12), pp. 13–18, ACM, Lyon, France, April 2012.

\bibitem{Krishnan1}
Internet evolution
\textit{https://atos.net/content/dam/global/ascent-whitepapers/ascent-whitepaper-internet-evolution.pdf}
\bibitem{Bernhard}
Bernhard Ager,Wolfgang Mhlbauer,Georgios Smaragdakis,Steve Uhlig
\textit{Web Content Cartography.}
\bibitem{Ager}
Bernhard Ager 
\textit{Impact of Location on Content Delivery}.
http://people.ee.ethz.ch/~bager/papers/A-ILCD-11.pdf
\bibitem{Frank}
Benjamin Frank, Ingmar Poese, Georgios Smaragdakis,
Anja Feldmann, Bruce M. Maggs, Steve Uhlig,
Vinay Aggarwal, Fabian Schneider
\textit{Collaboration Opportunities for
Content Delivery and Network Infrastructures}.
2013
\bibitem{Mike4}
P. Mockapetris
\textit{Domain Name System}.
https://www.ietf.org/rfc/rfc1034.txt

\bibitem{dns}
 Postel, Jon. 
 \textit{"Domain Name System Structure and Delegation"}
Network Working Group. Retrieved 7 February 2011.

\bibitem{RISTOL}
K RISTOL , D., AND M ONTULLI , L. 
\textit{HTTP State Management Mechanism}.
RFC 2109.
\bibitem{RISTOL1}
K RISTOL , D., AND M ONTULLI , L.
\textit{HTTP State Management Mechanism}.
RFC 2965.

\bibitem{alexa}
Alexa
\textit{http://www.alexa.com/topsites}

\bibitem{scrapy}
Scrapy
\textit{http://doc.scrapy.org}.
\bibitem{crawler}
\textit{Technology: How and Why We Crawl the Web}. 
Alexa. Archived from the original on April 2, 2014. Retrieved November 6, 2011.

\bibitem{Maier}
G. Maier, A. Feldmann, V. Paxson, and M. Allman.
\textit{On Dominant Characteristics of Residential Broadband Internet Traffic}.
In Proc. ACM IMC,2009.
\bibitem{Nygren}
Nygren, R. K. Sitaraman, and J. Sun. 
\textit{The Akamai Network:A Platform for High-performance Internet Applications}.
Syst. Rev., 44:219, August 2010.
\bibitem{Krishnan}
R. Krishnan, H. Madhyastha, S. Srinivasan, S. Jain,A. Krishnamurthy, T.
Anderson, and J. Gao. 
\textit{Moving Beyond End-to-end Path Information to Optimize CDN Performance}.
\bibitem{Yuval}
Yuval Shavitt, Udi Weinsberg.
\textit{Topological Trends of Internet Content Providers}.
SIMPLEX 12: Proceedings of the Fourth Annual Workshop on
Simplifying Complex Networks for Practitioners (2012): 13-18.
\bibitem{Xenofontas}
Xenofontas Dimitropoulos, Dmitri Krioukov, Marina Fomenkov, Bradley
Huffaker, Young Hyun, kc claffy, George Riley 
\textit{AS Relationships: Inference and Validation}.
SIGCOMM Computer Communications Review 37, no. 1(2007): 31-40.
\bibitem{Gerber}
A. Gerber and R. Doverspike.
\textit{Traffic Types and Growth in Backbone Networks}.
OFC/NFOEC, 2011.
\bibitem{Mike}
Mike Axelrod
\textit{The Value of Content Distribution Networks and Google Global Cache}.
\bibitem{Netflix Open Connect}
Netflix Open Connect
\textit{https://openconnect.netflix.com/en/}
\bibitem{Mike1}
\textit{http://www.hpl.hp.com/research/idl/papers/ranking/adamicglottometrics.pdf.}
\bibitem{Lada}
Lada A. Adamic ,Bernardo A. 
\textit{Huberman Zipfs law and the Internet} . 
Glottometrics 3, 2002,p 143-150
\bibitem{Lada1}
RIPE NCC
\textit{RIPE Routing Information Service}.
http://www.ripe.net/ris/.


\end{thebibliography}